Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2014-09-02 generate.tex
fig:breaking

\begin{figure}
	\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}[
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]
	\pgfplotscreateplotcyclelist{earthy}{%
	black,
	red!40!black,
	red!60!black,
	red!80!black,
	red,
	red!80!yellow,
	red!60!yellow,
	red!40!yellow,
	}
	\begin{groupplot}[
	group style={
			group name=g, group size=2 by 1,
			horizontal sep=4em,
			},
		width=0.5\columnwidth+1em,%
		height=10\baselineskip,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
%		\nextgroupplot[
%			xlabel={time (min)}, xmin=0,
%			ymin=0, ymax=1, ylabel={aspect ratio},
%			only marks,]
%		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
%		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};
		\nextgroupplot[
			xlabel=$q^2\sigma^2$, xmin=0,
			ylabel=$A\tau_B/q^2\sigma^2$, ymin=0, ymax=0.2, ytick={0,0.1,0.2},
			]
		\addplot[only marks] table[x expr=\thisrowno{0}^2, y expr=\thisrowno{1}/\thisrowno{0}^2] {155C.growth};
		\addplot[no marks, red, domain=1.6:7] {1.5*(1-0.115*x)/(1+3.62*x)};

@@

>>>>

\begin{figure}
	%\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}[
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]
	\pgfplotscreateplotcyclelist{earthy}{%
	black,
	red!40!black,
	red!60!black,
	red!80!black,
	red,
	red!80!yellow,
	red!60!yellow,
	red!40!yellow,
	}
	\begin{groupplot}[
	group style={
			group name=g, group size=2 by 1,
			horizontal sep=4em,
			},
		width=0.5\columnwidth+1em,%
		height=10\baselineskip,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
%		\nextgroupplot[
%			xlabel={time (min)}, xmin=0,
%			ymin=0, ymax=1, ylabel={aspect ratio},
%			only marks,]
%		\addplot table {155C_percolation_1645.aspect} node[below left] {$\lambda_3/\lambda_1$};
%		\addplot table[y index=3] {155C_percolation_1645.aspect} node[above left] {$\lambda_2/\lambda_1$};
		\nextgroupplot[
			xlabel=$q^2\sigma^2$, xmin=0,
			ylabel=$A\tau_B/q^2\sigma^2$, ymin=0, ymax=0.2, ytick={0,0.1,0.2},
			]
		\addplot[only marks] table[x expr=\thisrowno{0}^2, y expr=\thisrowno{1}/\thisrowno{0}^2] {155C.growth};
		\addplot[no marks, red, domain=1.6:7] {1.5*(1-0.115*x)/(1+3.62*x)};

@@

\begin{figure*}
\tikzset{external/force remake}
\tikzsetnextfilename{breaking}
\begin{tikzpicture}[
	lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
	]
	\begin{groupplot}[
	group style={
			group name=g, group size=1 by 2,
			%horizontal sep=4em,
			},
		width=0.25\textwidth,%
		height=8\baselineskip,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
		\nextgroupplot[
			height=9\baselineskip,%
			xlabel=$L$, ylabel={count},
			xmode=log, ymode=log,
			ymin=1, xmin=1,
			clip marker paths=true,
			]
			\addplot+[only marks] file {172A_broken_length.hist};
			\addplot+[only marks] file {170A_broken_length.hist};
			\addplot+[only marks,mark=asterisk, black] file {150A_broken_length.hist};
			\addplot[domain=1:32, no marks] {1e6/x^3} node[midway, above right] {-3};
			\addplot[domain=1:10, no marks] {1e4/x^4} node[midway, below left] {-4};

		\nextgroupplot[
			xlabel=$q_2$, ylabel={$P(q_2)$ [\%]},
			xmin=0,xmax=1,
			ymin=0,
			no marks
			]
			\addplot table[y expr=\thisrowno{1}*100] {150A_broken_q2.proba};
			\addplot table[y expr=\thisrowno{1}*100] {150A_broken_q2_L2.proba};
	\end{groupplot}

	\matrix[
		matrix of nodes, inner sep=0, %column sep=0.01\textwidth, 
		row sep=0.5em,
		matrix anchor=north west,
		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
		] (m){
		\SI{0}{\minute} & \SI{16}{\minute} & \SI{22}{\minute} & \SI{30.5}{\minute} & \SI{31}{\minute} & \SI{90}{\minute} \\
		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0000s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0032s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0043s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0061s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0062s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_particles_wireframe_t0180s.png}\\
		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0000s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0032s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0043s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0061s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0062s.png}&
		\includegraphics[width=0.13\textwidth]{breaking_wireframe_t0180s.png}\\
		};
	\node[lab] at (m.north west) {a};
	\node[lab] at (g c1r1.outer north west) {b};
	\node[lab] at (g c1r2.left of south west) {c};
\end{tikzpicture}
\caption{\textbf{Mechanical tension drives coarsening} 
\textbf{a} Reconstruction from experimental coordinates ($\phi=29~\%$, $c_p=\SI{0.7}{\gram\per\litre}$) of coarsening process geometry (top) and topology (bottom). Particles are drawn to scale and coloured by $q_2$ from blue (low) to red (high). The meshed surface is a Gaussian coarse-graining of the network pattern. The red line indicates the shortest on-graph path between the two particles of interest. 
\textbf{b} Number of bond breaking function of the future on-graph distance for three state points (after percolation): $\phi=8,\,18,\,29~\%$, $c_p=1.5,\,0.6,\,\SI{0.7}{\gram\per\litre}$ for \textcolor{blue}{$\bullet$}, \textcolor{red}{\tiny$\blacksquare$} and $*$ respectively.
\textbf{c} Probability for a bond to break during $3\tau_B$ function of bond-centred $q_2$ for all events (blue) and for events with $L>1$ (red) in the same sample as \textbf{a}.
}
\label{fig:breaking}
\end{figure*}
